Three-dimensional fluorophore orientation imaging with polarized multiview microscopy

### 2018-01-19 notes/2018-01-18-osa-abstract/abstract.tex
Refactoring and cleaning up.

\author{Talon Chandler, Min Guo, Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}
\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging and Bioengineering,\\ National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
\email{*talonchandler@talonchandler.com} %% email address is required

>>>>

\author{Talon Chandler, Min Guo, Shalin Mehta, Abhishek Kumar,\\ Hari Shroff, Rudolf Oldenbourg, Patrick J. La Rivi\`ere}

\address{Department of Radiology, University of Chicago, Chicago, Illinois 60637, USA.\\Section on High Resolution Optical Imaging, National Institute of Biomedical Imaging\\ and Bioengineering, National Institutes of Health, Bethesda, Maryland 20892, USA.\\ Chan Zuckerberg Biohub, San Francisco, California 94158, USA.\\ Bell Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Whitman Center, Marine Biological Laboratory, Woods Hole, Massachusetts 02543, USA.\\ Department of Physics, Brown University, Providence, Rhode Island 02912, USA.}
\email{*talonchandler@talonchandler.com} %% email address is required
